%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

%\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{paralist}
\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft\hoffset\leftline{\large\bf Shahwar Saleem} % Your name at the top
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt} % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft\hoffset\leftline{Unit 1003- 203 Lester Street, Waterloo ON, Canada}
  \begin{inparaitem} \itemsep 5pt % Reduce space between items
\item Email: shhawrleo@gmail.com
\item Tel: +92 (312) 521-4422
\end{inparaitem}
%----------------------------------------------------------------------------------------

\begin{resume}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Master of Science,} Computer Engineering \hfill May-2016 - Present \\
University of Waterloo \hfill Waterloo, Canada \\
Concentration: Computer Software

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Percentage: 90\% 
\item Supervisor: Dr. Krzysztof Czarnecki
\end{itemize}

{\sl Bachelor of Science,} Computer Engineering \hfill Sep-2009 - June-2013 \\
University of Engineering and Technology \hfill Lahore, Pakistan

\begin{itemize} \itemsep -2pt % Reduce space between items
\item GPA: 3.48/4.0
\item Advisor: Dr. Atif Alvi (Cambridge University) 
\item Thesis: Load Balancing of Computationally Intensive Algorithms using Beowulf Cluster

%\href{https://www.dropbox.com/s/3pfy6jsdewknzj1/Thesis.pdf}{Load Balancing of Computationally Intensive A%lgorithms using Beowulf Cluster}
\end{itemize}
 
%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNICAL SKILLS} 


\textbf{Languages \& Software:}
C, Java, Python, JavaScript, React.js, GraphQL, Bash Scripting, Assembly Language, Nucleus RTOS\\
\textbf{Operating Systems:} Linux, OS X, Windows\\
\textbf{Tools:} SVN, Git, JIRA, Asana, Slack, Fisheye Crucible, Planio

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Software Engineer (Freelancing)} \hfill May-2017 - Present \\
Different Web Development Startups based in San Jose, CA. 

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Working React.js based web application. 

\item Working on GraphQL baseed API backend. 
\end{itemize}

{\sl Graduate Research Assistant} \hfill May-2016 - Present \\
GSD Lab, University of Waterloo \hfill Waterloo, ON

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Working on autonomous car project
\item Leading system integration efforts regarding embedded components of the car.
\item Working actively with QNX RTOS on embedded boards.
\end{itemize}
 
{\sl Software Engineer } \hfill Nov-2014 - May-2015 \\
Mentor Graphics  \hfill Lahore, Pakistan
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Worked on Eclipse based IDEs ReadyStart and Codebench. 
\item Worked on Eclipse plug-ins and Eclipse GUI using SWT/JFace \& MVC work flow in Java. 
\item Added support for Kernel Awareness to visualize processes and core occupation on a multi-core architecture. (SMP and AMP)
\end{itemize} 

{\sl Embedded Software Engineer} \hfill Oct-2013 - Nov-2014 \\
Mentor Graphics \hfill Lahore, Pakistan
\begin{itemize}  \itemsep -2pt % Reduce space between items
\item Worked on Nucleus RTOS based Board Support Packages (BSPs)
\item Developed device drivers like I2C, LCD Display, SPI, Serial for Nucleus RTOS on ARM \& PPC Architecture.
\item Learned about debugging tools like JLink, BDI and MESP.
\end{itemize} 

%{\sl Embedded Research Intern} \hfill Apr-2013 - Jul-2013 \\
%Al-Khwarizmi Institute of Computer Science(R\&D) \hfill Lahore, Pakistan
%\begin{itemize} \itemsep -2pt % Reduce space between items
%\item Worked on type - II hypervisor.  
%\item Learned instruction translation mechanism from Guest OS to Host OS.
%\item Learned about debugging different instructions on Octeon 12 board.
%\end{itemize}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\section{GRADUATE PROJECTS}

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Autonomous Car Platoon using Fuzzy Logic and Neural Networks
\item Multiple-Producer Multiple-Consumer based Shortest Path Solving Server (Dijkstra's Algorithm and System Programming)
\item Prediction of Yelp rating based on user text reviews (Natural Language Processing techniques like Stemming, Vectorization, N-Grams)
\end{itemize}

\section{AWARDS} 

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Graduate Research Studentship - University of Waterloo - (2016 - 2018)
\item International Master's Student Award - University of Waterloo - (2016 - 2018)
\item National Talent Scholarship from Government of Pakistan (2009-2013)
\end{itemize}


\end{resume}
\end{document}
