%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

%\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{paralist}
\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft\hoffset\leftline{\large\bf Shahwar Saleem} % Your name at the top
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt} % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft\hoffset\leftline{256 Carlaw Pl, Waterloo ON N2J 3Y9}
  \begin{inparaitem} \itemsep 5pt % Reduce space between items
\item Email: saleemshahwar@gmail.com
\item Tel: +1 (226) 220-7123
\end{inparaitem}
%----------------------------------------------------------------------------------------

\begin{resume}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Master of Engineering} \hfill May-2016 - Aug-2018 \\
University of Waterloo \hfill Waterloo, Canada \\
Concentration: Deep Learning, Data Science

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Percentage: 88.62% 
%\item Supervisor: Dr. Krzysztof Czarnecki
%\item Thesis Topic: Run-time Risk Monitor for Autonomous Vehicles
\end{itemize}

{\sl Bachelor of Science,} Computer Engineering \hfill Sep-2009 - June-2013 \\
University of Engineering and Technology \hfill Lahore, Pakistan

\begin{itemize} \itemsep -2pt % Reduce space between items
\item GPA: 3.48/4.0
\item Advisor: Dr. Atif Alvi (Cambridge University) 
\item Thesis: Load Balancing of Computationally Intensive Algorithms using Beowulf Cluster

%\href{https://www.dropbox.com/s/3pfy6jsdewknzj1/Thesis.pdf}{Load Balancing of Computationally Intensive A%lgorithms using Beowulf Cluster}
\end{itemize}
 
%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

%{\sl Software Engineer (Freelancing)} \hfill Jan-2017 - Present \\
%Different Web Development Startups based in San Jose, CA.  \hfill Remote

{\sl Machine Learning Engineer} \hfill Aug-2018 - present \\
Pronavigator Technologies\hfill Waterloo, ON

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Working on Data pipelines and Deep learning algorithms to train insurance bots for insurance companies. Goal is to replace human insurance agents with conversational AI bots.

\end{itemize}

{\sl Graduate Research Student} \hfill May-2016 - Apr-2018 \\
Professor Krzysztof Czarnecki \\
WISE Lab, University of Waterloo \hfill Waterloo, ON

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Trained CNN architecture to detect camera occlusion on Autonomous Vehicle. Occlusion detection was reported to a ROS based architecture to warn system about non-friendly environment/situations for vehicle safety. The results were used in publication.
\
\item Formulated a Run-time risk monitoring architecture for risk assessment in Machine Learning components of Autonomous Vehicle. Currently being employed in Autonomoose of WISE Lab as risk monitoring system.

\item Partially worked on 3D - Object Detection on autonomous vehicle architecture. The name of the architecture was AVOD.

\item Lead Autonmoose Integration team in CES'17. Successfully delivered ROS ported on ARM architecture based RDrive boards from Renesas.
\end{itemize}
 
 
{\sl Machine Learning Engineer} \hfill September-2016 - Aug-2017 \\
Stowk Inc.  \hfill San Francisco Bay Area


\begin{itemize} \itemsep -2pt % Reduce space between items
\item  Design, experiment and maintenance of price prediction models based on RFs and NNs. Hands on experience with training neural networks for price prediction.
\item Architecture design of React Native app for Stowk.
\item Worked on GraphQL based API backend.
%\item HTML, CSS and SASS with Twitter Bootstrap 
\end{itemize} 
 
{\sl Software Engineer } \hfill Oct-2013 - May-2016 \\
Mentor Graphics  \hfill Lahore, Pakistan
\begin{itemize} \itemsep -2pt % Reduce space between items 
\item Design and implementation of Kernel Awareness to visualize processes and core occupation level on a multi-core architecture. (SMP and AMP)
\item Nucleus RTOS based Board Support Packages (BSPs). Developed Device drivers like I2C, LCD Display, SPI, Serial for Nucleus RTOS on ARM \& PPC Architecture.
\item Eclipse plug-ins, toolchain development and kernel issues.
\end{itemize} 


%{\sl Embedded Research Intern} \hfill Apr-2013 - Jul-2013 \\
%Al-Khwarizmi Institute of Computer Science(R\&D) \hfill Lahore, Pakistan
%\begin{itemize} \itemsep -2pt % Reduce space between items
%\item Worked on type - II hypervisor.  
%\item Learned instruction translation mechanism from Guest OS to Host OS.
%\item Learned about debugging different instructions on Octeon 12 board.
%\end{itemize}


\section{PUBLICATIONS} 

Co-Author, \textit{"An Automated Vehicle Safety Concept Based on Runtime Restriction of the Operational Design Domain"} , 2018 IEEE Intelligent Vehicles Symposium

\section{SKILLS} 


\textbf{Languages \& Software:}
RASA, C, TensorFlow, Keras, NLTK, Python, JavaScript, React.js, GraphQL, Bash Scripting, Nucleus RTOS\\
%\textbf{Operating Systems:} Linux, OS X, Windows\\
\textbf{Tools:} SVN, Git, JIRA, Asana, Slack, Fisheye Crucible, Planio
%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\section{GRADUATE PROJECTS}

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Autonomous Car Platoon using Fuzzy Logic and Neural Networks
\item Multiple-Producer Multiple-Consumer based Shortest Path Solving Server (Dijkstra's Algorithm and System Programming)
\item Prediction of Yelp rating based on user text reviews (Natural Language Processing techniques like Stemming, Vectorization, N-Grams)
\end{itemize}

\section{AWARDS} 

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Graduate Research Studentship - University of Waterloo - (2016 - 2018)
\item International Master's Student Award - University of Waterloo - (2016 - 2018)
\item National Talent Scholarship from Government of Pakistan (2009-2013)
\end{itemize}


\end{resume}
\end{document}
