%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Shahwar}{Saleem}{ \urlstyle{Well Balanced Combination of Data Science and Software Engineering} 
\href{mailto:saleemshahwar@gmail.com}{saleemshahwar@gmail.com} | 226.220.7123}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Waterloo}
\descript{MEng in Computer Engineering}
\location{August 2018 | Waterloo, ON \\ Cum. GPA: 89\%}
\sectionsep


\subsection{University of \\ Engineering and \\Technology}
\descript{BE in Computer Engineering}
\location{August 2013 | Lahore, Pakistan \\ Cum. GPA: 85\%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/shahwar9}{\custombold{shahwar9}} \\
LinkedIn://  \href{https://www.linkedin.com/in/shahwar-saleem-050ba93a/}{\custombold{shahwarsaleem}} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Software Engineering}
Tools of Software Engineering \\
Algorithm Design and Analysis\\
Safety Critical Embedded Systems \\
Operating Systems \\
Computer Programming Languages \\
Data Structures \\
Computer Networks \\
Data Bases \\
\sectionsep

\subsection{Data Science}
Knowledge Modelling and Analysis \\
Tools of Intelligent Systems Design \\
Research Topics: Machine Learning \\
Text Analytics (NLP) \\
Deep Learning Specialization (Coursera)
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming Languages}
\location{Over 5000 lines:}
\textbullet{} C \textbullet{} Python \textbullet{} JavaScript \\

\location{Over 1000 lines:}
\textbullet{} Java \textbullet{} MySQL \textbullet{} C++
\sectionsep
\subsection{Tools}
\textbullet{} Openshift \textbullet{} PySpark \textbullet{}  Docker \\
\textbullet{} Kubernetes \textbullet{} Jenkins \\
 \textbullet{} Git \textbullet{} JIRA \textbullet{} Slack 

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
%\subsection{University of Waterloo}
\subsubsection*{Graduate Research Studentship}
\subsubsection*{International Master's Student Award}

%\subsection{Government of Pakistan}
\subsubsection*{2009-2013 National Talent Scholarship}

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.63\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Borealis AI}
<<<<<<< HEAD:Shahwar_Saleem_2021-06.tex
\descript{| Machine Learning Software Engineer }
=======
\descript{| Software Engineer }
>>>>>>> master:Shahwar_Saleem_2020.tex
\location{July 2019 - Present | Waterloo, ON}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

<<<<<<< HEAD:Shahwar_Saleem_2021-06.tex
\item Designed/Implemented a solution for accessing data of different sorts from different storages like NAS, S3 etc. Data Access Platform enables researchers to efficiently access random data from O(100TB) datasets. The solution capitalizes on the typical Database idea of indexing, the difference is that this indexing is done by traversing File System on millions of files of the dataset.


\item Designed/Implemented robust Jenkins + Openshift based CI/CD pipeline for pip packages. This pipeline automated the package delivery to users through artifactory within Borealis AI. Integrated a versioning strategy with pipeline to streamline release process. Release process was cut down to automated minutes from hours of human intervention.

\item Responsible for vision and roadmap of a data access platform. On boarded 5-6 projects to use Data Access Platform. Data Accessing efforts of all these projects were brought down to a few commands and minutes in processing from hours and days of processing and lots of lines of code to write until researchers get to see the data.
=======
\item As part of Data Management team, designed a robust data ingestion and pre-processing pipeline for research and production environments. Developed reusable tools to handle O(TeraBytes) of data to be processed with PySpark and injested into research or production pipeline.

\item Developed and currently maintaining a Conda Package for internal dataset abstraction. The package testing is automated through Openshift and Jenkins.

\item Optimized fake data generation script from single process to multi process Python job. This brought time to generate 7TB of data from 12 days to just 15 hours.
>>>>>>> master:Shahwar_Saleem_2020.tex

\end{tightemize}
\sectionsep

\runsubsection{Pronavigator.io}
\descript{| Software Engineer (Machine Learning) }
\location{August 2018 - June 2019 | Kitchener, ON}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

\item Implemented complete migration from SVM pipeline to Deep Neural Network model pipeline after showing through a research report that NNs perform better as compared to SVMs.  This migration saved significant servers cost per month and gained a huge performance increase. 
<<<<<<< HEAD:Shahwar_Saleem_2021-06.tex

\item Improved the machine learning pipeline by implementing a Confusion Matrix tailored to text classification needs of NLU engine of Pronavigator. This provided a sight into correlations between different kinds of user messages. An accuracy performance increase of 10 to 15\% was evident because owing to more context driven confusion matrix data was cleaned accordingly.
=======
-
\item Improved the machine learning pipeline by implementing a Confusion Matrix tailored to text classification needs of NLU engine of Pronavigator. This provided a sight into correlations between different kinds of user messages. A performance increase of 7 to 10\% was evident because owing to more context driven confusion matrix data was cleaned accordingly.
>>>>>>> master:Shahwar_Saleem_2020.tex

\end{tightemize}
\sectionsep

%\runsubsection{Stowk, INC}
%\descript{| Machine Learning Engineer}
%\location{Sept 2016 - Aug 2017 | San Francisco Bay Area (Remote)}
%\begin{tightemize}
%\item  Design, experiment and maintenance of price prediction models based on RFs and NNs. Hands on experience with training neural networks for price prediction.
%\item Architecture design of React Native app for Stowk. Also worked on GraphQL based API backend.\end{tightemize}
%\sectionsep

\runsubsection{Mentor Graphics Corporation}
\descript{| Software Engineer}
\location{Oct 2013 - May 2016 | Lahore, Pakistan}
\begin{tightemize}

\item Improved visualization of processes on a multi-core architecture in RTOS by implementing a feature called Kernel Awareness. Kernel Awareness connected the core information of a process to pre-defined UI. Through this UI of Kernel Awareness, developers could clearly see state, memory utilization, affinity etc of each process which is critical in an RTOS.

\item Experienced developing different device drivers for Nucleus RTOS. (I2C, SPI, LCD, CAN etc drivers for ARM \& PPC Architectures)

\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications}
\runsubsection{Waterloo Intelligent Systems Engineering (WISE) Lab}
\descript{| Co-Author}
\location{Jan 2018}
\textit{"An Automated Vehicle Safety Concept Based on Runtime Restriction of the Operational Design Domain"} , 2018 IEEE Intelligent Vehicles Symposium

\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Graduate Projects} 

%\begin{tabular}{rll}



<<<<<<< HEAD:Shahwar_Saleem_2021-06.tex
%2018   &  Fake News Challenge Phase 1   &  \href{https://github.com/shahwar9/fakenewschallenge}{\custombold{Github}}\\
%2017   &  Prediction of Yelp rating based on user text reviews  &  \href{https://github.com/shahwar9/RatingsPrediction_NLP}{\custombold{Github}}\\
%2016 	& Autonomous Car Platoon (Fuzzy Logic and Neural Networks)    & \href{https://github.com/shahwar9/AutonomousCarPlatoon/}{\custombold{Github}}
%\end{tabular}
%\sectionsep
=======
2018   &  Fake News Challenge Phase 1   &  \href{https://github.com/shahwar9/fakenewschallenge}{\custombold{Github}}\\
2017   &  Prediction of Yelp rating based on user text reviews  &  \href{https://github.com/shahwar9/RatingsPrediction_NLP}{\custombold{Github}}\\
2016 	& Autonomous Car Platoon (Fuzzy Logic and Neural Networks)    & \href{https://github.com/shahwar9/AutonomousCarPlatoon/}{\custombold{Github}}
\end{tabular}
\sectionsep
>>>>>>> master:Shahwar_Saleem_2020.tex

\end{minipage} 
\end{document}